Fractional Types

### 2016-12-16 typespp.tex
structure of paper

@@

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Looping and Delooping}

add here

@@

Only non-trivial pairs are created by eta; they create ``synchronized'' uses combinators $c^k$ and $1/c^k$. The rest of the combinators can only replace these combinators by $\isotwo$-equivalent ones. Assoc is subtle: what if we have $\langle \order{c_1} , \langle \iorder{c_2} , \order{c_2} \rangle \rangle$; naive assoc would allow us to create a pair with unrelated combinators which cannot be eliminated using epsilon. But if assoc is constrained to maintain the invariant that only ``synchronized'' uses of combinators are ever paired together, everything works great.

@@

ccc have a notion of higher-order functions, trace, etc. Talk about these examples.
